SMT-Boosted Security Types for Low-Level MPC

### 2025-11-24 toplas26/sty.tex
checkpoint

\begin{definition}
  \label{def-genshares}
  We say that $\genshares$ is \emph{sound} iff given any $\prog,\Gamma,R : {OK}$
  and $\phi$ and $\rx{w}{\cid} \not \in R$ with $\genshares(\phi,\rx{w}{\cid}) =
  \phi_1,\phi_2$ and $\toeq{\prog} \models x_1 \eop \phi_1 \wedge x_2 \eop \phi_2$
  with $\secrets(\prog) = S$ and:
  $$
  \Gamma = \setit{[\phi_1^1,\phi_1^2] : \sharety, \ldots, [\phi_n^1,\phi_n^2] : \sharety}
  \cup \setit{\pubx{\phi_1} : \pubty,\ldots,\pubx{\phi_j} : \pubty} \cup
  \setit{\pubx{\phi^o_1} : \outty,\ldots,\pubx{\phi^o_k} : \outty}
  $$
  we have for all $a,b \in \setit{1,2}$:
  \begin{enumerate}[\hspace{5mm}i.]
    \item $\condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \setit{\phi_1^b,\ldots,\phi_n^b} \cup
      %\setit{\phi_1,\ldots,\phi_j}
      \setit{\phi^o_1,\ldots,\phi^o_k}}
    =
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \setit{\phi_1^b,\ldots,\phi_n^b,x_b} \cup
      %\setit{\phi_1,\ldots,\phi_j}
      \setit{\phi^o_1,\ldots,\phi^o_k}}$
    \item $\condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{\setit{\recon(x_1,x_2)}} =
      \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{\setit{\recon(x_1,x_2), x_b}}$
    \end{enumerate}
\end{definition}

>>>>

\begin{definition}
  \label{def-genshares}
  We say that $\genshares$ is \emph{sound} iff given any $\prog$ with
  $\vars(\prog) = S \cup V \cup O \cup R$
  and $\phi$ and $\rx{w}{\cid} \not \in R$ and $\genshares(\phi,\rx{w}{\cid}) =
  \phi_1,\phi_2$ we have for all $a \in \setit{1,2}$:
  $$
  \sep{\progd(\prog)}{(S \cup V \cup O \cup \setit{\phi})}{\setit{\phi_a}}
  $$
\end{definition}
